\section{Task Breakdown}

\subsection{Planning}
\begin{itemize}
    \item Define objectives, brainstorm ideas, and create a project plan.
    \item Decide on technologies to be used.
\end{itemize}

\subsection{UI Design}
\begin{itemize}
    \item Decide on a consistent theme, design and color scheme.
\end{itemize}
\begin{enumerate}
    \item Web App
    \begin{itemize}
        \item Create a wireframe for the web app in Figma.
        \item Create a non-functional prototype with dummy data.
    \end{itemize}
    \item Native App (Android and iOS)
    \begin{itemize}
        \item Create a wireframe for the web app in Figma.
        \item Create a non-functional prototype with dummy data.
    \end{itemize}
\end{enumerate}

\subsection{UX Design}
Only for the mobile app.
\begin{itemize}
    \item Integrate phone camera to scan barcodes.
    \item Use location services to track user's location.
    \item Integration with wearable devices.
    \item Work on social media integration.
    \item Work on push notifications.
\end{itemize}

\subsection{Backend Development}
\begin{itemize}
    \item Create database schemas.
    \item Handle user authentication.
    \item Create a REST API for the gym tracker.
    \item Create a REST API for the calorie counter.
\end{itemize}

\subsection{Merging Functionality}
\begin{itemize}
    \item Add functionality to the apps and remove dummy data.
    \item Integrate external APIs. (USDA Food Database, Google Fit, Google Maps, Adsense, etc.)
    \item Handle request errors.
\end{itemize}

\subsection{Testing and Deployment}
\begin{itemize}
    \item Test the apps on multiple devices and resolve bugs.
    \item Deploy the app on the Google Play Store and App Store.
    \item Deploy the web app on Vercel.
\end{itemize}

\clearpage